---
title: "Linear Multiple Regression + Spatial structure"
author: "Pauline Depoortere"
date: "02/12/2022"
output: pdf_document
---

#1. Datatable preparation 

I create a table in which, for my 2073 plots, there are my response and predictive variables (those chosen) from different sources of climate data.

Note: For demonstration purposes, the percentage of pioneer species is randomly generated here. In the actual dataset, this variable was derived from the CoForTraits database (https://dataverse.cirad.fr/dataset.xhtml?persistentId=doi:10.18167/DVN1/Y2BIZK), which compiles trait data for Central African tree species. The two R scripts used to calculate this metric from the original data are as "4_FieldDataInventories_Analyse_Temperament.R" and "5_PlotsMetrics_Analyse_Temperament.R".


```{r include=FALSE}

rm(list=ls()) 


setwd("C:/Users/u237004/Documents/1_Boulot_SC/2_Papier Pan/Final_Nature/Code/7_Modeles_bis_sans_montane/")
#Libraries
library(data.table) #is used to import and manipulate tables
library(broom)
library(ggplot2)
#library(dotwhisker) 
library(dplyr)

library(adespatial) 
library(spdep)
library(vegan)
library(textshape) 

library(janitor)

#Set the seed (pseudo-random number generator), for exact reproducibility
set.seed(2023)

#Load the data
data<-fread("Pantropical_dataset_2076plots_V2_N_55_1_SOIL.csv")
# pion<-fread("pourc_pionnier_Af.csv")
# 
# result <- merge(data, pion[, .(plot, Proportion)], by.x = "PLT_trois_bis", by.y = "plot", all.x = TRUE)
# result[is.na(Proportion)&Continent=="Africa",uniqueN(PLT_trois_bis)]
# 
# result<-result[Continent=="Africa"][!is.na(Proportion)]
# 
# data<-result

##FOR DEMONSTRATION########################################################################
data[, Proportion := runif(.N, min = 0, max = 100)]
########################################################################


summary(data)
#class(data)

data<-data[!elevation.y>=1000]
data<-data[!is.na(Bio1_WC)]
```

Comments: I have NA's for Year2. Otherwise there are no NAs in the response and predictive variables ;) 
##1.1. Number of plots per continent

```{r echo=FALSE}
data[,.(.N),by=Continent]
```



#2. Spatial structure 

### Check that each site is only present once:

```{r}
uniqueN(data, by="PLT_trois_bis")
```

### Quick visualisation of the sites in space:

```{r}
data %>% 
  ggplot(aes(LON, LAT)) +
  geom_point() +
  coord_fixed() +
  theme_classic()
```
###!!! Choice of the data climate source

```{r}
brut=data
data=data[,.(PLT_trois_bis,PLT_deux_bis,Ps,LAT,LON,Continent,Year,DBHqm,BA,SD,WD,WDba,AGB_Chave_eq7,AGB_Feld_Pan,AGB_Feld_Cont,AGB_Feld_Reg,sand,org,ph,slope,Bio1=Bio1_WC,Bio12=Bio12_WC,Bio15=Bio15_WC,Proportion)]

##Afrique 
data_Af<-data[Continent=="Africa",]
class(data_Af)


##AGB


##Pantropic
data_AGB_Cont<-data[!is.na(AGB_Feld_Cont)]
##Africa
data_Af_AGB_Cont<-data_AGB_Cont[Continent=="Africa",]
class(data_Af)

#Pantropic
data_AGB_Reg<-data[!is.na(AGB_Feld_Reg)]

##Afrique 
data_Af_AGB_Reg<-data_AGB_Reg[Continent=="Africa",]
class(data_Af)

rm(data)
rm(data_AGB_Reg)
rm(data_AGB_Cont)

```


##!!! Standardization of all predictor and/or response variables


```{r include=FALSE}

##Africa
data_Af[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Af[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Af[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Af[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Af[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Af[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Af[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]
data_Af[,Proportion:=as.vector(scale(Proportion, center=TRUE, scale=TRUE)),]


##AGB Cont#############################################################################################

##Africa
data_Af_AGB_Cont[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Af_AGB_Cont[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Af_AGB_Cont[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,Proportion:=as.vector(scale(Proportion, center=TRUE, scale=TRUE)),]

##AGB Reg##############################################################################################

##Africa
data_Af_AGB_Reg[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Af_AGB_Reg[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Af_AGB_Reg[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,Proportion:=as.vector(scale(Proportion, center=TRUE, scale=TRUE)),]
```


##2.1.Generation of a set of SWMs 

... from which the optimisation of the selection of both the SWM and the subset of MEM variables within it will be carried out:


We will test the two most contrasting graph-based criteria of connectivity as we have a irregular design (excluding the Delaunay triangulation to avoid edge effect issues), with a Gabriel graph and a minimum spanning tree. We will test these connectivity matrices without weighting the connexions and weighting them by the linear decreasing function of distance provided in the function (the further apart, the less two sites are connected or "exchange information").


```{r}
#source("listw.candidates_modif.R")
listw.candidates_modif<-function(coord, 
                               style = "B", 
                               nb = c("del", "gab", "rel", "mst", "pcnm", "dnear"),
                               d1 = 0, 
                               d2,
                               weights = c("binary", "flin", "fup", "fdown"),
                               y_fdown = 5, 
                               y_fup = 0.5,
                               nnmult = 10) {
  
  nb <- match.arg(nb, several.ok = TRUE)
  weights <- match.arg(weights, several.ok = TRUE)
  
  
  if (length(nb) == 0) 
    stop("No connectivity matrix selected")
  if (length(weights) == 0) 
    stop("No weighting matrix selected")
  
  if (anyNA(coord)) stop("NA entries in coord")
  
  coord.mat <- as.matrix(coord)
  xy.d1 <- dist(coord.mat)  
  
  res <- list()
  ## Manage the case of pcnm separately (as it is not concerned by weights)
  if ("pcnm" %in% nb) {
    f <- function(D, t) { 1 - (D / (4 * t))^2 }           # PCNM criterion
    lowlim <- give.thresh(xy.d1)
    matB <- dnearneigh(x = coord.mat, d1 = 0, d2 = (1 + sqrt(.Machine$double.eps)) * lowlim) ## add espsilon to ensure that all sites have neighbors
    res[[1]] <- nb2listw(matB, style = style, 
                         glist = lapply(nbdists(matB, coord.mat),
                                        f, t = lowlim))
    names(res) <- "DBEM_PCNM"
    nb <- nb[-match("pcnm", nb)]
    if (length(nb) == 0)
      return(res)
  }
  
  
  .addweights <- function(nb.object, nb.dist, coord.mat, weights, style, Prefix,
                          y_fdown, y_fup) {
    ## this utility function returns a list of listw objects created 
    ## using a single nb.object and several weights
    res <- list()
    res.names <- c()
    f1 <- function(D, dmax)     { 1 - (D/dmax) }       # Linear function
    f2 <- function(D, dmax, y)  { 1 - (D/dmax)^y }     # Concave-down function
    f3 <- function(D, y)        { 1 / D^y }            # Concave-up function
    
    if ("binary" %in% weights) {
      res <- c(res, list(nb2listw(nb.object, style = style)))
      res.names <- c(res.names, paste(Prefix, "Binary", sep = "_"))
    }
    
    if ("flin" %in% weights) {
      max.del <- max(unlist(nbdists(nb.object, coord.mat)))
      
      res <- c(res, list(nb2listw(nb.object, style = style, 
                                  glist = lapply(nb.dist, f1, dmax = max.del))))
      res.names <- c(res.names, paste(Prefix, "Linear", sep = "_"))
    }
    
    if ("fdown" %in% weights) {
      max.del <- max(unlist(nbdists(nb.object, coord.mat)))
      for (i in y_fdown) {
        res <- c(res, list(nb2listw(nb.object, style = style, 
                                    glist = lapply(nbdists(nb.object, coord.mat), 
                                                   f2, y = i, dmax = max.del))))
        res.names <- c(res.names, paste(Prefix, "Down", i, sep = "_"))
        
      }
    }
    
    
    if ("fup" %in% weights) {
      for (i in y_fup) {
        res <- c(res, list(nb2listw(nb.object, style = style, 
                                    glist = lapply(nbdists(nb.object, coord.mat), 
                                                   f3, y = i))))
        res.names <- c(res.names, paste(Prefix, "Up", i, sep = "_"))
        
      }
    }
    
    names(res) <- res.names
    return(res)
  }
  
  
  
  if ("del" %in% nb) {
    nb.object <- tri2nb(coord.mat)
    nb.dist <- nbdists(nb.object, coord.mat)
    res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                              Prefix = "Delaunay", y_fdown, y_fup))
  }
  
  
  if ("gab" %in% nb) {
    nb.object <- graph2nb(gabrielneigh(coord.mat, nnmult = nnmult), sym = TRUE)
    nb.dist <- nbdists(nb.object, coord.mat)
    res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                              Prefix = "Gabriel", y_fdown, y_fup))
  }
  
  
  if ("rel" %in% nb) {
    nb.object <- graph2nb(relativeneigh(coord.mat, nnmult = nnmult), sym = TRUE)
    nb.dist <- nbdists(nb.object, coord.mat)
    res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                              Prefix = "Relative", y_fdown, y_fup))
  }
  
  if ("mst" %in% nb) {
    nb.object <- mst.nb(xy.d1)
    nb.dist <- nbdists(nb.object, coord.mat)
    res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                              Prefix = "MST", y_fdown, y_fup))
  }
  
  if ("dnear" %in% nb) {
    # If "dnear" and no value specified for d2, then d2 is set to be the
    # largest edge of the minimum spanning tree (minimum distance keeping all points connected)
    if (missing(d2))
      d2 <- (1 + sqrt(.Machine$double.eps)) * give.thresh(xy.d1)
    
    nb.dnear <- lapply(d2, dnearneigh, x = coord.mat, d1 = d1)
    for (nb.i in 1:length(nb.dnear)) {
      nb.object <- nb.dnear[[nb.i]]
      nb.dist <- nbdists(nb.object, coord.mat)
      res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                                Prefix = paste("Dnear", round(d2[nb.i], 2), sep = ""), y_fdown, y_fup))
      
      
    }
    
  }
  
  return(res)
  
}



listw.candidates<-listw.candidates_modif

```



```{r}


#########################################################################################################################################################
##Africa
#########################################################################################################################################################

###Table of spatial coordinates:
xy_Af <- data_Af %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Af <- listw.candidates(xy_Af, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Af)


#########################################################################################################################################################
##AGB_Cont
#########################################################################################################################################################


##Africa

###Table of spatial coordinates:
xy_Af_AGB_Cont <- data_Af_AGB_Cont %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Af_AGB_Cont <- listw.candidates(xy_Af_AGB_Cont, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Af_AGB_Cont)

#########################################################################################################################################################
##AGB_Reg
#########################################################################################################################################################



##Africa

###Table of spatial coordinates:
xy_Af_AGB_Reg <- data_Af_AGB_Reg %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Af_AGB_Reg <- listw.candidates(xy_Af_AGB_Reg, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Af_AGB_Reg)



```

Comments : Message for Africa "zero sum general weightszero sum general weights" ? David Bauman said to not take this message into account ;)


##2.2. MEMs : Optimisation procedure (Bauman et al. 2018, Ecology)

A SWM as well as a subset of MEM variables need to be selected at this stage.
As discussed in Bauman et al. (2018, Ecography), the univariate / multivariate nature of the 
response data as well as the type of question / objective should guide the choice of the type of 
spatial eigenvector selection method.

###a) MIR : Minimum number of components

In the present case, we will use the MIR criterion (see Ecography paper), hence favoring the minimisation of the model residual spatial autocorrelation using the smallest subset of spatial predictors possible. 


#####DBHqm :

```{r}

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Africa

###MLR
DBHqmAf=lm(DBHqm~Bio1+Bio12+Bio15+slope+sand+ph+org+Proportion, data=data_Af)
summary(DBHqmAf)

###Residuals
res_DBHqmAf<-residuals(DBHqmAf)

###Get the best MEMs
select_DBHqmAf<-listw.select(res_DBHqmAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_DBHqmAf$best.id#4
select_DBHqmAf$best$MEM.select
select_DBHqmAf$candidates$N.var[select_DBHqmAf$best.id]# 8 MEMs
select_DBHqmAf$candidates

bestMEM_DBHqmAf<-bind_cols(data_Af %>%
                      dplyr::select(DBHqm,Bio1,Bio12,Bio15,slope,sand,ph,org,Proportion),
                      select_DBHqmAf$best$MEM.select) 


rm(select_DBHqmAf)




rm(res_DBHqmAf)



```

#####BA :

```{r}

##Africa

###MLR
BAAf=lm(BA~Bio1+Bio12+Bio15+slope+sand+ph+org+Proportion, data=data_Af)
summary(BAAf)

###Residuals
res_BAAf<-residuals(BAAf)

###Get the best MEMs
select_BAAf<-listw.select(res_BAAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_BAAf$best.id#4
select_BAAf$best$MEM.select
select_BAAf$candidates$N.var[select_BAAf$best.id]# 8 MEMs
select_BAAf$candidates

bestMEM_BAAf<-bind_cols(data_Af %>%
                      dplyr::select(BA,Bio1,Bio12,Bio15,slope,sand,ph,org,Proportion),
                      select_BAAf$best$MEM.select) 

rm(select_BAAf)




rm(res_BAAf)


```

#####SD :

```{r}

##Africa

###MLR
SDAf=lm(SD~Bio1+Bio12+Bio15+slope+sand+ph+org+Proportion, data=data_Af)
summary(SDAf)

###Residuals
res_SDAf<-residuals(SDAf)

###Get the best MEMs
select_SDAf<-listw.select(res_SDAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_SDAf$best.id#4
select_SDAf$best$MEM.select
select_SDAf$candidates$N.var[select_SDAf$best.id]# 8 MEMs
select_SDAf$candidates

bestMEM_SDAf<-bind_cols(data_Af %>%
                      dplyr::select(SD,Bio1,Bio12,Bio15,slope,sand,ph,org,Proportion),
                      select_SDAf$best$MEM.select) 


rm(select_SDAf)



rm(res_SDAf)

```

#####WDba :

```{r}

##Africa

###MLR
WDbaAf=lm(WDba~Bio1+Bio12+Bio15+slope+sand+ph+org+Proportion, data=data_Af)
summary(WDbaAf)

###Residuals
res_WDbaAf<-residuals(WDbaAf)

###Get the best MEMs
select_WDbaAf<-listw.select(res_WDbaAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_WDbaAf$best.id#4
select_WDbaAf$best$MEM.select
select_WDbaAf$candidates$N.var[select_WDbaAf$best.id]# 8 MEMs
select_WDbaAf$candidates

bestMEM_WDbaAf<-bind_cols(data_Af %>%
                      dplyr::select(WDba,Bio1,Bio12,Bio15,slope,sand,ph,org,Proportion),
                      select_WDbaAf$best$MEM.select) 


rm(select_WDbaAf)



rm(res_WDbaAf)

```


#####AGB Feld Pan : 

```{r}
##Africa

###MLR
AGB_Feld_PanAf=lm(AGB_Feld_Pan~Bio1+Bio12+Bio15+slope+sand+ph+org+Proportion, data=data_Af)
summary(AGB_Feld_PanAf)

###Residuals
res_AGB_Feld_PanAf<-residuals(AGB_Feld_PanAf)

###Get the best MEMs
select_AGB_Feld_PanAf<-listw.select(res_AGB_Feld_PanAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_PanAf$best.id#4
select_AGB_Feld_PanAf$best$MEM.select
select_AGB_Feld_PanAf$candidates$N.var[select_AGB_Feld_PanAf$best.id]# 8 MEMs
select_AGB_Feld_PanAf$candidates

bestMEM_AGB_Feld_PanAf<-bind_cols(data_Af %>%
                      dplyr::select(AGB_Feld_Pan,Bio1,Bio12,Bio15,slope,sand,ph,org,Proportion),
                      select_AGB_Feld_PanAf$best$MEM.select) 





rm(select_AGB_Feld_PanAf)


rm(res_AGB_Feld_PanAf)

```

#####AGB Feld Cont : 

```{r}

##Africa

###MLR
AGB_Feld_ContAf=lm(AGB_Feld_Cont~Bio1+Bio12+Bio15+slope+sand+ph+org+Proportion, data=data_Af_AGB_Cont)
summary(AGB_Feld_ContAf)

###Residuals
res_AGB_Feld_ContAf<-residuals(AGB_Feld_ContAf)

###Get the best MEMs
select_AGB_Feld_ContAf<-listw.select(res_AGB_Feld_ContAf, swm_candidates_Af_AGB_Cont, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_ContAf$best.id#4
select_AGB_Feld_ContAf$best$MEM.select
select_AGB_Feld_ContAf$candidates$N.var[select_AGB_Feld_ContAf$best.id]# 8 MEMs
select_AGB_Feld_ContAf$candidates

bestMEM_AGB_Feld_ContAf<-bind_cols(data_Af_AGB_Cont %>%
                      dplyr::select(AGB_Feld_Cont,Bio1,Bio12,Bio15,slope,sand,ph,org,Proportion),
                      select_AGB_Feld_ContAf$best$MEM.select) 




rm(select_AGB_Feld_ContAf)



rm(res_AGB_Feld_ContAf)
```

#####AGB Feld Reg : 

```{r}
##Africa

###MLR
AGB_Feld_RegAf=lm(AGB_Feld_Reg~Bio1+Bio12+Bio15+slope+sand+ph+org+Proportion, data=data_Af_AGB_Reg)
summary(AGB_Feld_RegAf)

###Residuals
res_AGB_Feld_RegAf<-residuals(AGB_Feld_RegAf)

###Get the best MEMs
select_AGB_Feld_RegAf<-listw.select(res_AGB_Feld_RegAf, swm_candidates_Af_AGB_Reg, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_RegAf$best.id#4
select_AGB_Feld_RegAf$best$MEM.select
select_AGB_Feld_RegAf$candidates$N.var[select_AGB_Feld_RegAf$best.id]# 8 MEMs
select_AGB_Feld_RegAf$candidates

bestMEM_AGB_Feld_RegAf<-bind_cols(data_Af_AGB_Reg %>%
                      dplyr::select(AGB_Feld_Reg,Bio1,Bio12,Bio15,slope,sand,ph,org,Proportion),
                      select_AGB_Feld_RegAf$best$MEM.select) 


rm(select_AGB_Feld_RegAf)




rm(res_AGB_Feld_RegAf)

```

##Export
```{r include=FALSE}
fwrite(bestMEM_DBHqmAf,"bestMEM_DBHqmAf_WC_af.csv")

fwrite(bestMEM_BAAf,"bestMEM_BAAf_WC_af.csv")

fwrite(bestMEM_SDAf,"bestMEM_SDAf_WC_af.csv")

fwrite(bestMEM_WDbaAf,"bestMEM_WDbaAf_WC_af.csv")

fwrite(bestMEM_AGB_Feld_PanAf,"bestMEM_AGB_Feld_PanAf_WC_af.csv")

fwrite(bestMEM_AGB_Feld_ContAf,"bestMEM_AGB_Feld_ContAf_WC_af.csv")

fwrite(bestMEM_AGB_Feld_RegAf,"bestMEM_AGB_Feld_RegAf_WC_af.csv")
```

##Importation
```{r include=FALSE}
#bestMEM_DBHqmAf<-fread("bestMEM_DBHqmAf_WC_af.csv")

#bestMEM_BAAf<-fread("bestMEM_BAAf_WC_af.csv")

#bestMEM_SDAf<-fread("bestMEM_SDAf_WC_af.csv")

#bestMEM_WDbaAf<-fread("bestMEM_WDbaAf_WC_af.csv")

#bestMEM_AGB_Feld_PanAf<-fread("bestMEM_AGB_Feld_PanAf_WC_af.csv")

#bestMEM_AGB_Feld_ContAf<-fread("bestMEM_AGB_Feld_ContAf_WC_af.csv")
#bestMEM_AGB_Feld_RegAf<-fread("bestMEM_AGB_Feld_RegAf_WC_af.csv")
```

#3. Multiple Linear Regression 

##3.1. DBHqm

###a) MLR Model with MEMs

```{r include=FALSE}


##Africa

#
DBHqmAf_F=lm(DBHqm~., data=bestMEM_DBHqmAf)
summary(DBHqmAf_F)

rse<-summary(DBHqmAf_F)$sigma
r_squared<-summary(DBHqmAf_F)$r.squared
mean<-data_Af[,mean(DBHqm),]
results<-tidy(DBHqmAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:9][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="DBH_qm",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(results[,.(rep, sub_rep, area,Bio1, Bio12, Bio15, slope, sand, ph, org,Proportion, r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(DBHqmAf_F)$coefficients[,4]))
test<-test[2:9]
test[, `:=`(rep = "SC" , sub_rep = "DBHqm", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org","Proportion"))][,V1:=NULL,]
end2<-test
rm(test)
```


##3.2. BA

###a) MLR Model with MEMs

```{r include=FALSE}

##Africa

#
BAAf_F=lm(BA~., data=bestMEM_BAAf)
summary(BAAf_F)

rse<-summary(BAAf_F)$sigma
r_squared<-summary(BAAf_F)$r.squared
mean<-data_Af[,mean(BA),]
results<-tidy(BAAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:9][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="BA",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,Proportion, r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(BAAf_F)$coefficients[,4]))
test<-test[2:9]
test[, `:=`(rep = "SC" , sub_rep = "BA", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org","Proportion"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)



```


##3.3. SD

###a) MLR Model with MEMs

```{r include=FALSE}

##Africa

#
SDAf_F=lm(SD~., data=bestMEM_SDAf)
summary(SDAf_F)

rse<-summary(SDAf_F)$sigma
r_squared<-summary(SDAf_F)$r.squared
mean<-data_Af[,mean(SD),]
results<-tidy(SDAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:9][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="SD",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,Proportion,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(SDAf_F)$coefficients[,4]))
test<-test[2:9]
test[, `:=`(rep = "SC" , sub_rep = "SD", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org","Proportion"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


```

##3.4. WDba

###a)  MLR Model with MEMs

```{r include=FALSE}


##Africa

#
WDbaAf_F=lm(WDba~., data=bestMEM_WDbaAf)
summary(WDbaAf_F)

rse<-summary(WDbaAf_F)$sigma
r_squared<-summary(WDbaAf_F)$r.squared
mean<-data_Af[,mean(WDba),]
results<-tidy(WDbaAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:9][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="WDba",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,Proportion,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(WDbaAf_F)$coefficients[,4]))
test<-test[2:9]
test[, `:=`(rep = "SC" , sub_rep = "WDba", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org","Proportion"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


```



##3.6. AGB_Feld_Pan

###a) MLR Model with MEMs

```{r include=FALSE}

##Africa

#
AGB_Feld_PanAf_F=lm(AGB_Feld_Pan~., data=bestMEM_AGB_Feld_PanAf)
summary(AGB_Feld_PanAf_F)

rse<-summary(AGB_Feld_PanAf_F)$sigma
r_squared<-summary(AGB_Feld_PanAf_F)$r.squared
mean<-data_Af[,mean(AGB_Feld_Pan),]
results<-tidy(AGB_Feld_PanAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:9][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Pan",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,Proportion,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_PanAf_F)$coefficients[,4]))
test<-test[2:9]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Pan", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org","Proportion"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)




```


##3.7. AGB_Feld_Cont

###a) MLR Model with MEMs

```{r include=FALSE}

##Africa

#
AGB_Feld_ContAf_F=lm(AGB_Feld_Cont~., data=bestMEM_AGB_Feld_ContAf)
summary(AGB_Feld_ContAf_F)

rse<-summary(AGB_Feld_ContAf_F)$sigma
r_squared<-summary(AGB_Feld_ContAf_F)$r.squared
mean<-data_Af_AGB_Cont[,mean(AGB_Feld_Cont),]
results<-tidy(AGB_Feld_ContAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:9][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Cont",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,Proportion,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_ContAf_F)$coefficients[,4]))
test<-test[2:9]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Cont", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org","Proportion"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


```

##3.8. AGB_Feld_Re


###a) MLR Model with MEMs

```{r include=FALSE}

##Africa

#
AGB_Feld_RegAf_F=lm(AGB_Feld_Reg~., data=bestMEM_AGB_Feld_RegAf)
summary(AGB_Feld_RegAf_F)


rse<-summary(AGB_Feld_RegAf_F)$sigma
r_squared<-summary(AGB_Feld_RegAf_F)$r.squared
mean<-data_Af_AGB_Reg[,mean(AGB_Feld_Reg),]
results<-tidy(AGB_Feld_RegAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:9][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Reg",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,Proportion,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_RegAf_F)$coefficients[,4]))
test<-test[2:9]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Reg", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org","Proportion"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)
```

#Je sors le tableau 

```{r}
end[,source:="WC",]
end2[,source:="WC",]

fwrite(end,"end_stand_WC_af.csv")
fwrite(end2,"end2_stand_WC_af.csv")


```

```{r}
```