---
title: "Linear Multiple Regression + Spatial structure"
author: "Pauline Depoortere"
date: "02/12/2022"
output: pdf_document
---

#1. Datatable preparation 

I import my final table in which, for all my plots, there are my response and predictive variables (those chosen) from different sources of climate data.

```{r include=FALSE}

rm(list=ls()) 

setwd("C:/Users/u237004/Documents/1_Boulot_SC/2_Papier Pan/Final_Nature/Code/7_Modeles_bis_sans_montane/")

#Libraries
library(data.table) #is used to import and manipulate tables
library(broom)
library(ggplot2)
#library(dotwhisker) 
library(dplyr)

library(adespatial) 
library(spdep)
library(vegan)
library(textshape) 

library(janitor)

#Set the seed (pseudo-random number generator), for exact reproducibility
set.seed(2023)

#Load the data
data<-fread("Pantropical_dataset_2076plots_V2_N_55_1_SOIL.csv")

summary(data)
#class(data)

#Remove plots located above 1000 m elevation

data<-data[!elevation.y>=1000]
data<-data[!is.na(Bio1_WC)]
```

Comments:  there are no NAs in the response and predictive variables ;) 
##1.1. Number of plots per continent

```{r echo=FALSE}
data[,.(.N),by=Continent]
```



#2. Spatial structure 

### Check that each site is only present once:

```{r}
uniqueN(data, by="PLT_trois_bis")
```

### Quick visualisation of the sites in space:

```{r}
data %>% 
  ggplot(aes(LON, LAT)) +
  geom_point() +
  coord_fixed() +
  theme_classic()
```
###!!! Choice of the data climate source

```{r}
brut=data
data=data[,.(PLT_trois_bis,PLT_deux_bis,Ps,LAT,LON,Continent,Year,DBHqm,BA,SD,WD,WDba,AGB_Chave_eq7,AGB_Feld_Pan,AGB_Feld_Cont,AGB_Feld_Reg,sand,org,ph,slope,Bio1=Bio1_WC,Bio12=Bio12_WC,Bio15=Bio15_WC)]

##Afrique 
data_Af<-data[Continent=="Africa",]
class(data_Af)
##Asie 
data_As<-data[Continent=="Eurasia"]
##South America 
data_SA<-data[Continent=="South America"]
##Oceania
data_Oc<-data[Continent=="Oceania"]
##North America 
data_NA<-data[Continent=="North America"]


##AGB


##Pantropic
data_AGB_Cont<-data[!is.na(AGB_Feld_Cont)]
##Africa
data_Af_AGB_Cont<-data_AGB_Cont[Continent=="Africa",]
class(data_Af)
##Asia
data_As_AGB_Cont<-data_AGB_Cont[Continent=="Eurasia"]
##South America 
data_SA_AGB_Cont<-data_AGB_Cont[Continent=="South America"]
##Oceania
data_Oc_AGB_Cont<-data_AGB_Cont[Continent=="Oceania"]
##North America 
data_NA_AGB_Cont<-data_AGB_Cont[Continent=="North America"]


data_AGB_Reg<-data[!is.na(AGB_Feld_Reg)]

##Afrique 
data_Af_AGB_Reg<-data_AGB_Reg[Continent=="Africa",]
class(data_Af)
##Asie 
data_As_AGB_Reg<-data_AGB_Reg[Continent=="Eurasia"]
##South America 
data_SA_AGB_Reg<-data_AGB_Reg[Continent=="South America"]
##Oceania
data_Oc_AGB_Reg<-data_AGB_Reg[Continent=="Oceania"]
##North America 
data_NA_AGB_Reg<-data_AGB_Reg[Continent=="North America"]

rm(data)
rm(data_AGB_Reg)
rm(data_AGB_Cont)
```


##!!! Standardization of all predictor and/or response variables


```{r include=FALSE}


##Africa
data_Af[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Af[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Af[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Af[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Af[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Af[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Af[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]

##South America
data_SA[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_SA[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_SA[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_SA[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_SA[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_SA[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_SA[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]

##North America
data_NA[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_NA[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_NA[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_NA[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_NA[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_NA[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_NA[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]


##Oceania
data_Oc[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Oc[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Oc[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Oc[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Oc[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Oc[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Oc[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]


##Eurasia
data_As[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_As[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_As[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_As[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_As[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_As[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_As[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]



##AGB Cont#############################################################################################


##Africa
data_Af_AGB_Cont[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Af_AGB_Cont[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Af_AGB_Cont[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Af_AGB_Cont[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]

##South America
data_SA_AGB_Cont[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_SA_AGB_Cont[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_SA_AGB_Cont[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_SA_AGB_Cont[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_SA_AGB_Cont[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_SA_AGB_Cont[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_SA_AGB_Cont[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]

##North America
data_NA_AGB_Cont[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_NA_AGB_Cont[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_NA_AGB_Cont[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_NA_AGB_Cont[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_NA_AGB_Cont[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_NA_AGB_Cont[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_NA_AGB_Cont[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]


##Oceania
data_Oc_AGB_Cont[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Oc_AGB_Cont[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Oc_AGB_Cont[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Oc_AGB_Cont[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Oc_AGB_Cont[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Oc_AGB_Cont[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Oc_AGB_Cont[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]


##Eurasia
data_As_AGB_Cont[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_As_AGB_Cont[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_As_AGB_Cont[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_As_AGB_Cont[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_As_AGB_Cont[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_As_AGB_Cont[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_As_AGB_Cont[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]

##AGB Reg##############################################################################################

##Africa
data_Af_AGB_Reg[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Af_AGB_Reg[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Af_AGB_Reg[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Af_AGB_Reg[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]

##South America
data_SA_AGB_Reg[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_SA_AGB_Reg[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_SA_AGB_Reg[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_SA_AGB_Reg[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_SA_AGB_Reg[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_SA_AGB_Reg[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_SA_AGB_Reg[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]

##North America
data_NA_AGB_Reg[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_NA_AGB_Reg[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_NA_AGB_Reg[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_NA_AGB_Reg[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_NA_AGB_Reg[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_NA_AGB_Reg[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_NA_AGB_Reg[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]


##Oceania
data_Oc_AGB_Reg[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_Oc_AGB_Reg[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_Oc_AGB_Reg[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_Oc_AGB_Reg[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_Oc_AGB_Reg[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_Oc_AGB_Reg[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_Oc_AGB_Reg[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]


##Eurasia
data_As_AGB_Reg[,Bio1:=as.vector(scale(Bio1, center=TRUE, scale=TRUE)),]
data_As_AGB_Reg[,Bio15:=as.vector(scale(Bio15, center=TRUE, scale=TRUE)),]
data_As_AGB_Reg[,Bio12:=as.vector(scale(Bio12, center=TRUE, scale=TRUE)),]

data_As_AGB_Reg[,sand:=as.vector(scale(sand, center=TRUE, scale=TRUE)),]
data_As_AGB_Reg[,org:=as.vector(scale(org, center=TRUE, scale=TRUE)),]
data_As_AGB_Reg[,ph:=as.vector(scale(ph, center=TRUE, scale=TRUE)),]

data_As_AGB_Reg[,slope:=as.vector(scale(slope, center=TRUE, scale=TRUE)),]

```


##2.1.Generation of a set of SWMs 

... from which the optimisation of the selection of both the SWM and the subset of MEM variables within it will be carried out:


We will test the two most contrasting graph-based criteria of connectivity as we have a irregular design (excluding the Delaunay triangulation to avoid edge effect issues), with a Gabriel graph and a minimum spanning tree. We will test these connectivity matrices without weighting the connexions and weighting them by the linear decreasing function of distance provided in the function (the further apart, the less two sites are connected or "exchange information").


```{r}
#source("listw.candidates_modif.R")
listw.candidates_modif<-function(coord, 
                               style = "B", 
                               nb = c("del", "gab", "rel", "mst", "pcnm", "dnear"),
                               d1 = 0, 
                               d2,
                               weights = c("binary", "flin", "fup", "fdown"),
                               y_fdown = 5, 
                               y_fup = 0.5,
                               nnmult = 10) {
  
  nb <- match.arg(nb, several.ok = TRUE)
  weights <- match.arg(weights, several.ok = TRUE)
  
  
  if (length(nb) == 0) 
    stop("No connectivity matrix selected")
  if (length(weights) == 0) 
    stop("No weighting matrix selected")
  
  if (anyNA(coord)) stop("NA entries in coord")
  
  coord.mat <- as.matrix(coord)
  xy.d1 <- dist(coord.mat)  
  
  res <- list()
  ## Manage the case of pcnm separately (as it is not concerned by weights)
  if ("pcnm" %in% nb) {
    f <- function(D, t) { 1 - (D / (4 * t))^2 }           # PCNM criterion
    lowlim <- give.thresh(xy.d1)
    matB <- dnearneigh(x = coord.mat, d1 = 0, d2 = (1 + sqrt(.Machine$double.eps)) * lowlim) ## add espsilon to ensure that all sites have neighbors
    res[[1]] <- nb2listw(matB, style = style, 
                         glist = lapply(nbdists(matB, coord.mat),
                                        f, t = lowlim))
    names(res) <- "DBEM_PCNM"
    nb <- nb[-match("pcnm", nb)]
    if (length(nb) == 0)
      return(res)
  }
  
  
  .addweights <- function(nb.object, nb.dist, coord.mat, weights, style, Prefix,
                          y_fdown, y_fup) {
    ## this utility function returns a list of listw objects created 
    ## using a single nb.object and several weights
    res <- list()
    res.names <- c()
    f1 <- function(D, dmax)     { 1 - (D/dmax) }       # Linear function
    f2 <- function(D, dmax, y)  { 1 - (D/dmax)^y }     # Concave-down function
    f3 <- function(D, y)        { 1 / D^y }            # Concave-up function
    
    if ("binary" %in% weights) {
      res <- c(res, list(nb2listw(nb.object, style = style)))
      res.names <- c(res.names, paste(Prefix, "Binary", sep = "_"))
    }
    
    if ("flin" %in% weights) {
      max.del <- max(unlist(nbdists(nb.object, coord.mat)))
      
      res <- c(res, list(nb2listw(nb.object, style = style, 
                                  glist = lapply(nb.dist, f1, dmax = max.del))))
      res.names <- c(res.names, paste(Prefix, "Linear", sep = "_"))
    }
    
    if ("fdown" %in% weights) {
      max.del <- max(unlist(nbdists(nb.object, coord.mat)))
      for (i in y_fdown) {
        res <- c(res, list(nb2listw(nb.object, style = style, 
                                    glist = lapply(nbdists(nb.object, coord.mat), 
                                                   f2, y = i, dmax = max.del))))
        res.names <- c(res.names, paste(Prefix, "Down", i, sep = "_"))
        
      }
    }
    
    
    if ("fup" %in% weights) {
      for (i in y_fup) {
        res <- c(res, list(nb2listw(nb.object, style = style, 
                                    glist = lapply(nbdists(nb.object, coord.mat), 
                                                   f3, y = i))))
        res.names <- c(res.names, paste(Prefix, "Up", i, sep = "_"))
        
      }
    }
    
    names(res) <- res.names
    return(res)
  }
  
  
  
  if ("del" %in% nb) {
    nb.object <- tri2nb(coord.mat)
    nb.dist <- nbdists(nb.object, coord.mat)
    res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                              Prefix = "Delaunay", y_fdown, y_fup))
  }
  
  
  if ("gab" %in% nb) {
    nb.object <- graph2nb(gabrielneigh(coord.mat, nnmult = nnmult), sym = TRUE)
    nb.dist <- nbdists(nb.object, coord.mat)
    res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                              Prefix = "Gabriel", y_fdown, y_fup))
  }
  
  
  if ("rel" %in% nb) {
    nb.object <- graph2nb(relativeneigh(coord.mat, nnmult = nnmult), sym = TRUE)
    nb.dist <- nbdists(nb.object, coord.mat)
    res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                              Prefix = "Relative", y_fdown, y_fup))
  }
  
  if ("mst" %in% nb) {
    nb.object <- mst.nb(xy.d1)
    nb.dist <- nbdists(nb.object, coord.mat)
    res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                              Prefix = "MST", y_fdown, y_fup))
  }
  
  if ("dnear" %in% nb) {
    # If "dnear" and no value specified for d2, then d2 is set to be the
    # largest edge of the minimum spanning tree (minimum distance keeping all points connected)
    if (missing(d2))
      d2 <- (1 + sqrt(.Machine$double.eps)) * give.thresh(xy.d1)
    
    nb.dnear <- lapply(d2, dnearneigh, x = coord.mat, d1 = d1)
    for (nb.i in 1:length(nb.dnear)) {
      nb.object <- nb.dnear[[nb.i]]
      nb.dist <- nbdists(nb.object, coord.mat)
      res <- c(res, .addweights(nb.object, nb.dist, coord.mat, weights, style, 
                                Prefix = paste("Dnear", round(d2[nb.i], 2), sep = ""), y_fdown, y_fup))
      
      
    }
    
  }
  
  return(res)
  
}



listw.candidates<-listw.candidates_modif

```



```{r}

#########################################################################################################################################################
##Africa
#########################################################################################################################################################

###Table of spatial coordinates:
xy_Af <- data_Af %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Af <- listw.candidates(xy_Af, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Af)

#########################################################################################################################################################
##Asie 
#########################################################################################################################################################

###Table of spatial coordinates:
xy_As <- data_As %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_As <- listw.candidates(xy_As, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_As)

#########################################################################################################################################################
##South America 
#########################################################################################################################################################

###Table of spatial coordinates:
xy_SA <- data_SA %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_SA <- listw.candidates(xy_SA, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_SA)

#########################################################################################################################################################
##North America 
#########################################################################################################################################################

###Table of spatial coordinates:
xy_NA <- data_NA %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_NA <- listw.candidates(xy_NA, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_NA)

#########################################################################################################################################################
##Oceania
#########################################################################################################################################################

###Table of spatial coordinates:
xy_Oc <- data_Oc %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Oc <- listw.candidates(xy_Oc, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Oc)


#########################################################################################################################################################
##AGB_Cont
#########################################################################################################################################################

##Africa

###Table of spatial coordinates:
xy_Af_AGB_Cont <- data_Af_AGB_Cont %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Af_AGB_Cont <- listw.candidates(xy_Af_AGB_Cont, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Af_AGB_Cont)

##Asia

###Table of spatial coordinates:
xy_As_AGB_Cont <- data_As_AGB_Cont %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_As_AGB_Cont <- listw.candidates(xy_As_AGB_Cont, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_As_AGB_Cont)

##South America 

###Table of spatial coordinates:
xy_SA_AGB_Cont <- data_SA_AGB_Cont %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_SA_AGB_Cont <- listw.candidates(xy_SA_AGB_Cont, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_SA_AGB_Cont)


##Oceania

###Table of spatial coordinates:
xy_Oc_AGB_Cont <- data_Oc_AGB_Cont %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Oc_AGB_Cont <- listw.candidates(xy_Oc_AGB_Cont, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Oc_AGB_Cont)

#########################################################################################################################################################
##AGB_Reg
#########################################################################################################################################################


##Africa

###Table of spatial coordinates:
xy_Af_AGB_Reg <- data_Af_AGB_Reg %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Af_AGB_Reg <- listw.candidates(xy_Af_AGB_Reg, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Af_AGB_Reg)

##Asia

###Table of spatial coordinates:
xy_As_AGB_Reg <- data_As_AGB_Reg %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_As_AGB_Reg <- listw.candidates(xy_As_AGB_Reg, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_As_AGB_Reg)

##South America 

###Table of spatial coordinates:
xy_SA_AGB_Reg <- data_SA_AGB_Reg %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_SA_AGB_Reg <- listw.candidates(xy_SA_AGB_Reg, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_SA_AGB_Reg)


##Oceania

###Table of spatial coordinates:
xy_Oc_AGB_Reg <- data_Oc_AGB_Reg %>% 
  column_to_rownames("PLT_trois_bis") %>% 
  dplyr::select(LON, LAT)

###SWMs
swm_candidates_Oc_AGB_Reg <- listw.candidates(xy_Oc_AGB_Reg, nb = c('gab', 'mst'), weights = c('binary', 'flin'))
rm(xy_Oc_AGB_Reg)


```

Comments : Message for Africa "zero sum general weightszero sum general weights" ? David Bauman said to not take this message into account ;)


##2.2. MEMs : Optimisation procedure (Bauman et al. 2018, Ecology)

A SWM as well as a subset of MEM variables need to be selected at this stage.
As discussed in Bauman et al. (2018, Ecography), the univariate / multivariate nature of the 
response data as well as the type of question / objective should guide the choice of the type of 
spatial eigenvector selection method.

###a) MIR : Minimum number of components

In the present case, we will use the MIR criterion (see Ecography paper), hence favoring the minimisation of the model residual spatial autocorrelation using the smallest subset of spatial predictors possible. 


#####DBHqm :

```{r}


###################################################################################################################
###################################################################################################################
###################################################################################################################
##Africa

###MLR
DBHqmAf=lm(DBHqm~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Af)
summary(DBHqmAf)

###Residuals
res_DBHqmAf<-residuals(DBHqmAf)

###Get the best MEMs
select_DBHqmAf<-listw.select(res_DBHqmAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_DBHqmAf$best.id#4
select_DBHqmAf$best$MEM.select
select_DBHqmAf$candidates$N.var[select_DBHqmAf$best.id]# 8 MEMs
select_DBHqmAf$candidates

bestMEM_DBHqmAf<-cbind(data_Af %>%
                      dplyr::select(DBHqm,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_DBHqmAf$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##South-America

###MLR
DBHqmSA=lm(DBHqm~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_SA)
summary(DBHqmSA)

###Residuals
res_DBHqmSA<-residuals(DBHqmSA)

###Get the best MEMs
select_DBHqmSA<-listw.select(res_DBHqmSA, swm_candidates_SA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_DBHqmSA$best.id#2
select_DBHqmSA$best$MEM.select
select_DBHqmSA$candidates$N.var[select_DBHqmSA$best.id]# 19 MEMs
select_DBHqmSA$candidates

bestMEM_DBHqmSA<-cbind(data_SA %>%
                      dplyr::select(DBHqm,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_DBHqmSA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##Asia 

###MLR
DBHqmAs=lm(DBHqm~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_As)
summary(DBHqmAs)

###Residuals
res_DBHqmAs<-residuals(DBHqmAs)

###Get the best MEMs
select_DBHqmAs<-listw.select(res_DBHqmAs, swm_candidates_As, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_DBHqmAs$best.id
select_DBHqmAs$best$MEM.select
select_DBHqmAs$candidates$N.var[select_DBHqmAs$best.id]
select_DBHqmAs$candidates

bestMEM_DBHqmAs<-cbind(data_As %>%
                      dplyr::select(DBHqm,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_DBHqmAs$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Oceania 

###MLR
DBHqmOc=lm(DBHqm~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Oc)
summary(DBHqmOc)

###Residuals
res_DBHqmOc<-residuals(DBHqmOc)

###Get the best MEMs
select_DBHqmOc<-listw.select(res_DBHqmOc, swm_candidates_Oc, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_DBHqmOc$best.id
select_DBHqmOc$best$MEM.select
select_DBHqmOc$candidates$N.var[select_DBHqmOc$best.id]
select_DBHqmOc$candidates

bestMEM_DBHqmOc<-cbind(data_Oc %>%
                      dplyr::select(DBHqm,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_DBHqmOc$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################


###################################################################################################################
###################################################################################################################
###################################################################################################################
##North America

###MLR
DBHqmNA=lm(DBHqm~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_NA)
summary(DBHqmNA)

###Residuals
res_DBHqmNA<-residuals(DBHqmNA)

###Get the best MEMs
select_DBHqmNA<-listw.select(res_DBHqmNA, swm_candidates_NA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_DBHqmNA$best.id
select_DBHqmNA$best$MEM.select
select_DBHqmNA$candidates$N.var[select_DBHqmNA$best.id]
select_DBHqmNA$candidates

bestMEM_DBHqmNA<-cbind(data_NA %>%
                      dplyr::select(DBHqm,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_DBHqmNA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
#Clean the environment



rm(select_DBHqmAf)
rm(select_DBHqmSA)
rm(select_DBHqmAs)
rm(select_DBHqmNA)
rm(select_DBHqmOc)


rm(res_DBHqmAf)
rm(res_DBHqmSA)
rm(res_DBHqmAs)
rm(res_DBHqmNA)
rm(res_DBHqmOc)


```

#####BA :

```{r}

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Africa

###MLR
BAAf=lm(BA~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Af)
summary(BAAf)

###Residuals
res_BAAf<-residuals(BAAf)

###Get the best MEMs
select_BAAf<-listw.select(res_BAAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_BAAf$best.id#4
select_BAAf$best$MEM.select
select_BAAf$candidates$N.var[select_BAAf$best.id]# 8 MEMs
select_BAAf$candidates

bestMEM_BAAf<-cbind(data_Af %>%
                      dplyr::select(BA,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_BAAf$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##South-America

###MLR
BASA=lm(BA~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_SA)
summary(BASA)

###Residuals
res_BASA<-residuals(BASA)

###Get the best MEMs
select_BASA<-listw.select(res_BASA, swm_candidates_SA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_BASA$best.id#2
select_BASA$best$MEM.select
select_BASA$candidates$N.var[select_BASA$best.id]# 19 MEMs
select_BASA$candidates

bestMEM_BASA<-cbind(data_SA %>%
                      dplyr::select(BA,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_BASA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##Asia 

###MLR
BAAs=lm(BA~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_As)
summary(BAAs)

###Residuals
res_BAAs<-residuals(BAAs)

###Get the best MEMs
select_BAAs<-listw.select(res_BAAs, swm_candidates_As, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_BAAs$best.id
select_BAAs$best$MEM.select
select_BAAs$candidates$N.var[select_BAAs$best.id]
select_BAAs$candidates

bestMEM_BAAs<-cbind(data_As %>%
                      dplyr::select(BA,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_BAAs$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Oceania 

###MLR
BAOc=lm(BA~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Oc)
summary(BAOc)

###Residuals
res_BAOc<-residuals(BAOc)

###Get the best MEMs
select_BAOc<-listw.select(res_BAOc, swm_candidates_Oc, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_BAOc$best.id
select_BAOc$best$MEM.select
select_BAOc$candidates$N.var[select_BAOc$best.id]
select_BAOc$candidates

bestMEM_BAOc<-cbind(data_Oc %>%
                      dplyr::select(BA,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_BAOc$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################


###################################################################################################################
###################################################################################################################
###################################################################################################################
##North America

###MLR
BANA=lm(BA~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_NA)
summary(BANA)

###Residuals
res_BANA<-residuals(BANA)

###Get the best MEMs
select_BANA<-listw.select(res_BANA, swm_candidates_NA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_BANA$best.id
select_BANA$best$MEM.select
select_BANA$candidates$N.var[select_BANA$best.id]
select_BANA$candidates

bestMEM_BANA<-cbind(data_NA %>%
                      dplyr::select(BA,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_BANA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
#Clean the environment



rm(select_BAAf)
rm(select_BASA)
rm(select_BAAs)
rm(select_BAOc)
rm(select_BANA)

rm(res_BAAf)
rm(res_BASA)
rm(res_BAAs)
rm(res_BAOc)
rm(res_BANA)

```

#####SD :

```{r}


###################################################################################################################
###################################################################################################################
###################################################################################################################
##Africa

###MLR
SDAf=lm(SD~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Af)
summary(SDAf)

###Residuals
res_SDAf<-residuals(SDAf)

###Get the best MEMs
select_SDAf<-listw.select(res_SDAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_SDAf$best.id#4
select_SDAf$best$MEM.select
select_SDAf$candidates$N.var[select_SDAf$best.id]# 8 MEMs
select_SDAf$candidates

bestMEM_SDAf<-cbind(data_Af %>%
                      dplyr::select(SD,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_SDAf$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##South-America

###MLR
SDSA=lm(SD~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_SA)
summary(SDSA)

###Residuals
res_SDSA<-residuals(SDSA)

###Get the best MEMs
select_SDSA<-listw.select(res_SDSA, swm_candidates_SA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_SDSA$best.id#2
select_SDSA$best$MEM.select
select_SDSA$candidates$N.var[select_SDSA$best.id]# 19 MEMs
select_SDSA$candidates

bestMEM_SDSA<-cbind(data_SA %>%
                      dplyr::select(SD,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_SDSA$best$MEM.select)
###################################################################################################################
###################################################################################################################
###################################################################################################################
##Asia 

###MLR
SDAs=lm(SD~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_As)
summary(SDAs)

###Residuals
res_SDAs<-residuals(SDAs)

###Get the best MEMs
select_SDAs<-listw.select(res_SDAs, swm_candidates_As, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_SDAs$best.id
select_SDAs$best$MEM.select
select_SDAs$candidates$N.var[select_SDAs$best.id]
select_SDAs$candidates

bestMEM_SDAs<-cbind(data_As %>%
                      dplyr::select(SD,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_SDAs$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Oceania

###MLR
SDOc=lm(SD~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Oc)
summary(SDOc)

###Residuals
res_SDOc<-residuals(SDOc)

###Get the best MEMs
select_SDOc<-listw.select(res_SDOc, swm_candidates_Oc, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_SDOc$best.id
select_SDOc$best$MEM.select
select_SDOc$candidates$N.var[select_SDOc$best.id]
select_SDOc$candidates

bestMEM_SDOc<-cbind(data_Oc %>%
                      dplyr::select(SD,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_SDOc$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################


###################################################################################################################
###################################################################################################################
###################################################################################################################
##North America

###MLR
SDNA=lm(SD~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_NA)
summary(SDNA)

###Residuals
res_SDNA<-residuals(SDNA)

###Get the best MEMs
select_SDNA<-listw.select(res_SDNA, swm_candidates_NA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_SDNA$best.id
select_SDNA$best$MEM.select
select_SDNA$candidates$N.var[select_SDNA$best.id]
select_SDNA$candidates

bestMEM_SDNA<-cbind(data_NA %>%
                      dplyr::select(SD,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_SDNA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
#Clean the environment


rm(select_SDAf)
rm(select_SDSA)
rm(select_SDAs)
rm(select_SDOc)
rm(select_SDNA)



rm(res_SDAf)
rm(res_SDSA)
rm(res_SDAs)
rm(res_SDOc)
rm(res_SDNA)

```

#####WDba :

```{r}

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Africa

###MLR
WDbaAf=lm(WDba~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Af)
summary(WDbaAf)

###Residuals
res_WDbaAf<-residuals(WDbaAf)

###Get the best MEMs
select_WDbaAf<-listw.select(res_WDbaAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_WDbaAf$best.id#4
select_WDbaAf$best$MEM.select
select_WDbaAf$candidates$N.var[select_WDbaAf$best.id]# 8 MEMs
select_WDbaAf$candidates

bestMEM_WDbaAf<-cbind(data_Af %>%
                      dplyr::select(WDba,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_WDbaAf$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##South-America

###MLR
WDbaSA=lm(WDba~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_SA)
summary(WDbaSA)

###Residuals
res_WDbaSA<-residuals(WDbaSA)

###Get the best MEMs
select_WDbaSA<-listw.select(res_WDbaSA, swm_candidates_SA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_WDbaSA$best.id#2
select_WDbaSA$best$MEM.select
select_WDbaSA$candidates$N.var[select_WDbaSA$best.id]# 19 MEMs
select_WDbaSA$candidates

bestMEM_WDbaSA<-cbind(data_SA %>%
                      dplyr::select(WDba,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_WDbaSA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##Asia 

###MLR
WDbaAs=lm(WDba~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_As)
summary(WDbaAs)

###Residuals
res_WDbaAs<-residuals(WDbaAs)

###Get the best MEMs
select_WDbaAs<-listw.select(res_WDbaAs, swm_candidates_As, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_WDbaAs$best.id
select_WDbaAs$best$MEM.select
select_WDbaAs$candidates$N.var[select_WDbaAs$best.id]
select_WDbaAs$candidates

bestMEM_WDbaAs<-cbind(data_As %>%
                      dplyr::select(WDba,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_WDbaAs$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################


###################################################################################################################
###################################################################################################################
###################################################################################################################
##Oceania

###MLR
WDbaOc=lm(WDba~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Oc)
summary(WDbaOc)

###Residuals
res_WDbaOc<-residuals(WDbaOc)

###Get the best MEMs
select_WDbaOc<-listw.select(res_WDbaOc, swm_candidates_Oc, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_WDbaOc$best.id
select_WDbaOc$best$MEM.select
select_WDbaOc$candidates$N.var[select_WDbaOc$best.id]
select_WDbaOc$candidates

bestMEM_WDbaOc<-cbind(data_Oc %>%
                      dplyr::select(WDba,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_WDbaOc$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################
###################################################################################################################
##North America

###MLR
WDbaNA=lm(WDba~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_NA)
summary(WDbaNA)

###Residuals
res_WDbaNA<-residuals(WDbaNA)

###Get the best MEMs
select_WDbaNA<-listw.select(res_WDbaNA, swm_candidates_NA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_WDbaNA$best.id
select_WDbaNA$best$MEM.select
select_WDbaNA$candidates$N.var[select_WDbaNA$best.id]
select_WDbaNA$candidates

bestMEM_WDbaNA<-cbind(data_NA %>%
                      dplyr::select(WDba,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_WDbaNA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
#Clean the environment


rm(select_WDbaAf)
rm(select_WDbaSA)
rm(select_WDbaAs)
rm(select_WDbaOc)
rm(select_WDbaNA)


rm(res_WDbaAf)
rm(res_WDbaSA)
rm(res_WDbaAs)
rm(res_WDbaOc)
rm(res_WDbaNA)

```


#####AGB Feld Pan : 

```{r}



###################################################################################################################
###################################################################################################################
###################################################################################################################
##Africa

###MLR
AGB_Feld_PanAf=lm(AGB_Feld_Pan~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Af)
summary(AGB_Feld_PanAf)

###Residuals
res_AGB_Feld_PanAf<-residuals(AGB_Feld_PanAf)

###Get the best MEMs
select_AGB_Feld_PanAf<-listw.select(res_AGB_Feld_PanAf, swm_candidates_Af, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_PanAf$best.id#4
select_AGB_Feld_PanAf$best$MEM.select
select_AGB_Feld_PanAf$candidates$N.var[select_AGB_Feld_PanAf$best.id]# 8 MEMs
select_AGB_Feld_PanAf$candidates

bestMEM_AGB_Feld_PanAf<-cbind(data_Af %>%
                      dplyr::select(AGB_Feld_Pan,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_PanAf$best$MEM.select) 



###################################################################################################################
###################################################################################################################
###################################################################################################################
##South-America

###MLR
AGB_Feld_PanSA=lm(AGB_Feld_Pan~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_SA)
summary(AGB_Feld_PanSA)

###Residuals
res_AGB_Feld_PanSA<-residuals(AGB_Feld_PanSA)

###Get the best MEMs
select_AGB_Feld_PanSA<-listw.select(res_AGB_Feld_PanSA, swm_candidates_SA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_PanSA$best.id#2
select_AGB_Feld_PanSA$best$MEM.select
select_AGB_Feld_PanSA$candidates$N.var[select_AGB_Feld_PanSA$best.id]# 19 MEMs
select_AGB_Feld_PanSA$candidates

bestMEM_AGB_Feld_PanSA<-cbind(data_SA %>%
                      dplyr::select(AGB_Feld_Pan,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_PanSA$best$MEM.select) 


###################################################################################################################
###################################################################################################################
###################################################################################################################
##Asia 

###MLR
AGB_Feld_PanAs=lm(AGB_Feld_Pan~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_As)
summary(AGB_Feld_PanAs)

###Residuals
res_AGB_Feld_PanAs<-residuals(AGB_Feld_PanAs)

###Get the best MEMs
select_AGB_Feld_PanAs<-listw.select(res_AGB_Feld_PanAs, swm_candidates_As, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_PanAs$best.id
select_AGB_Feld_PanAs$best$MEM.select
select_AGB_Feld_PanAs$candidates$N.var[select_AGB_Feld_PanAs$best.id]
select_AGB_Feld_PanAs$candidates

bestMEM_AGB_Feld_PanAs<-cbind(data_As %>%
                      dplyr::select(AGB_Feld_Pan,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_PanAs$best$MEM.select) 


###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Oceania

###MLR
AGB_Feld_PanOc=lm(AGB_Feld_Pan~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Oc)
summary(AGB_Feld_PanOc)

###Residuals
res_AGB_Feld_PanOc<-residuals(AGB_Feld_PanOc)

###Get the best MEMs
select_AGB_Feld_PanOc<-listw.select(res_AGB_Feld_PanOc, swm_candidates_Oc, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_PanOc$best.id
select_AGB_Feld_PanOc$best$MEM.select
select_AGB_Feld_PanOc$candidates$N.var[select_AGB_Feld_PanOc$best.id]
select_AGB_Feld_PanOc$candidates

bestMEM_AGB_Feld_PanOc<-cbind(data_Oc %>%
                      dplyr::select(AGB_Feld_Pan,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_PanOc$best$MEM.select) 


###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################
###################################################################################################################
##North AMerica

###MLR
AGB_Feld_PanNA=lm(AGB_Feld_Pan~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_NA)
summary(AGB_Feld_PanNA)

###Residuals
res_AGB_Feld_PanNA<-residuals(AGB_Feld_PanNA)

###Get the best MEMs
select_AGB_Feld_PanNA<-listw.select(res_AGB_Feld_PanNA, swm_candidates_NA, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_PanNA$best.id
select_AGB_Feld_PanNA$best$MEM.select
select_AGB_Feld_PanNA$candidates$N.var[select_AGB_Feld_PanNA$best.id]
select_AGB_Feld_PanNA$candidates

bestMEM_AGB_Feld_PanNA<-cbind(data_NA %>%
                      dplyr::select(AGB_Feld_Pan,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_PanNA$best$MEM.select) 


###################################################################################################################
###################################################################################################################
###################################################################################################################
#Clean the environment



rm(select_AGB_Feld_PanAf)
rm(select_AGB_Feld_PanSA)
rm(select_AGB_Feld_PanAs)
rm(select_AGB_Feld_PanOc)
rm(select_AGB_Feld_PanNA)


rm(res_AGB_Feld_PanAf)
rm(res_AGB_Feld_PanSA)
rm(res_AGB_Feld_PanAs)
rm(res_AGB_Feld_PanOc)
rm(res_AGB_Feld_PanNA)


```

#####AGB Feld Cont : 

```{r}

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Africa

###MLR
AGB_Feld_ContAf=lm(AGB_Feld_Cont~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Af_AGB_Cont)
summary(AGB_Feld_ContAf)

###Residuals
res_AGB_Feld_ContAf<-residuals(AGB_Feld_ContAf)

###Get the best MEMs
select_AGB_Feld_ContAf<-listw.select(res_AGB_Feld_ContAf, swm_candidates_Af_AGB_Cont, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_ContAf$best.id#4
select_AGB_Feld_ContAf$best$MEM.select
select_AGB_Feld_ContAf$candidates$N.var[select_AGB_Feld_ContAf$best.id]# 8 MEMs
select_AGB_Feld_ContAf$candidates

bestMEM_AGB_Feld_ContAf<-cbind(data_Af_AGB_Cont %>%
                      dplyr::select(AGB_Feld_Cont,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_ContAf$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##South-America

###MLR
AGB_Feld_ContSA=lm(AGB_Feld_Cont~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_SA_AGB_Cont)
summary(AGB_Feld_ContSA)

###Residuals
res_AGB_Feld_ContSA<-residuals(AGB_Feld_ContSA)

###Get the best MEMs
select_AGB_Feld_ContSA<-listw.select(res_AGB_Feld_ContSA, swm_candidates_SA_AGB_Cont, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_ContSA$best.id#2
select_AGB_Feld_ContSA$best$MEM.select
select_AGB_Feld_ContSA$candidates$N.var[select_AGB_Feld_ContSA$best.id]# 19 MEMs
select_AGB_Feld_ContSA$candidates

bestMEM_AGB_Feld_ContSA<-cbind(data_SA_AGB_Cont %>%
                      dplyr::select(AGB_Feld_Cont,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_ContSA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##Asia 

###MLR
AGB_Feld_ContAs=lm(AGB_Feld_Cont~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_As_AGB_Cont)
summary(AGB_Feld_ContAs)

###Residuals
res_AGB_Feld_ContAs<-residuals(AGB_Feld_ContAs)

###Get the best MEMs
select_AGB_Feld_ContAs<-listw.select(res_AGB_Feld_ContAs, swm_candidates_As_AGB_Cont, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_ContAs$best.id
select_AGB_Feld_ContAs$best$MEM.select
select_AGB_Feld_ContAs$candidates$N.var[select_AGB_Feld_ContAs$best.id]
select_AGB_Feld_ContAs$candidates

bestMEM_AGB_Feld_ContAs<-cbind(data_As_AGB_Cont %>%
                      dplyr::select(AGB_Feld_Cont,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_ContAs$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Oceania

###MLR
AGB_Feld_ContOc=lm(AGB_Feld_Cont~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Oc_AGB_Cont)
summary(AGB_Feld_ContOc)

###Residuals
res_AGB_Feld_ContOc<-residuals(AGB_Feld_ContOc)

###Get the best MEMs
select_AGB_Feld_ContOc<-listw.select(res_AGB_Feld_ContOc, swm_candidates_Oc_AGB_Cont, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_ContOc$best.id
select_AGB_Feld_ContOc$best$MEM.select
select_AGB_Feld_ContOc$candidates$N.var[select_AGB_Feld_ContOc$best.id]
select_AGB_Feld_ContOc$candidates

bestMEM_AGB_Feld_ContOc<-cbind(data_Oc_AGB_Cont %>%
                      dplyr::select(AGB_Feld_Cont,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_ContOc$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################

#Clean the environment



rm(select_AGB_Feld_ContAf)
rm(select_AGB_Feld_ContSA)
rm(select_AGB_Feld_ContAs)
rm(select_AGB_Feld_ContOc)

rm(res_AGB_Feld_ContAf)
rm(res_AGB_Feld_ContSA)
rm(res_AGB_Feld_ContAs)
rm(res_AGB_Feld_ContOc)

```

#####AGB Feld Reg : 

```{r}


###################################################################################################################
###################################################################################################################
###################################################################################################################
##Africa

###MLR
AGB_Feld_RegAf=lm(AGB_Feld_Reg~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Af_AGB_Reg)
summary(AGB_Feld_RegAf)

###Residuals
res_AGB_Feld_RegAf<-residuals(AGB_Feld_RegAf)

###Get the best MEMs
select_AGB_Feld_RegAf<-listw.select(res_AGB_Feld_RegAf, swm_candidates_Af_AGB_Reg, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_RegAf$best.id#4
select_AGB_Feld_RegAf$best$MEM.select
select_AGB_Feld_RegAf$candidates$N.var[select_AGB_Feld_RegAf$best.id]# 8 MEMs
select_AGB_Feld_RegAf$candidates

bestMEM_AGB_Feld_RegAf<-cbind(data_Af_AGB_Reg %>%
                      dplyr::select(AGB_Feld_Reg,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_RegAf$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##South-America

###MLR
AGB_Feld_RegSA=lm(AGB_Feld_Reg~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_SA_AGB_Reg)
summary(AGB_Feld_RegSA)

###Residuals
res_AGB_Feld_RegSA<-residuals(AGB_Feld_RegSA)

###Get the best MEMs
select_AGB_Feld_RegSA<-listw.select(res_AGB_Feld_RegSA, swm_candidates_SA_AGB_Reg, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_RegSA$best.id#2
select_AGB_Feld_RegSA$best$MEM.select
select_AGB_Feld_RegSA$candidates$N.var[select_AGB_Feld_RegSA$best.id]# 19 MEMs
select_AGB_Feld_RegSA$candidates

bestMEM_AGB_Feld_RegSA<-cbind(data_SA_AGB_Reg %>%
                      dplyr::select(AGB_Feld_Reg,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_RegSA$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################
##Asia 

###MLR
AGB_Feld_RegAs=lm(AGB_Feld_Reg~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_As_AGB_Reg)
summary(AGB_Feld_RegAs)

###Residuals
res_AGB_Feld_RegAs<-residuals(AGB_Feld_RegAs)

###Get the best MEMs
select_AGB_Feld_RegAs<-listw.select(res_AGB_Feld_RegAs, swm_candidates_As_AGB_Reg, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_RegAs$best.id
select_AGB_Feld_RegAs$best$MEM.select
select_AGB_Feld_RegAs$candidates$N.var[select_AGB_Feld_RegAs$best.id]
select_AGB_Feld_RegAs$candidates

bestMEM_AGB_Feld_RegAs<-cbind(data_As_AGB_Reg %>%
                      dplyr::select(AGB_Feld_Reg,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_RegAs$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
###################################################################################################################
###################################################################################################################
##Oceania

###MLR
AGB_Feld_RegOc=lm(AGB_Feld_Reg~Bio1+Bio12+Bio15+slope+sand+ph+org, data=data_Oc_AGB_Reg)
summary(AGB_Feld_RegOc)

###Residuals
res_AGB_Feld_RegOc<-residuals(AGB_Feld_RegOc)

###Get the best MEMs
select_AGB_Feld_RegOc<-listw.select(res_AGB_Feld_RegOc, swm_candidates_Oc_AGB_Reg, MEM.autocor = "positive", 
                         p.adjust = TRUE, method = "MIR", verbose = TRUE)

select_AGB_Feld_RegOc$best.id
select_AGB_Feld_RegOc$best$MEM.select
select_AGB_Feld_RegOc$candidates$N.var[select_AGB_Feld_RegOc$best.id]
select_AGB_Feld_RegOc$candidates

bestMEM_AGB_Feld_RegOc<-cbind(data_Oc_AGB_Reg %>%
                      dplyr::select(AGB_Feld_Reg,Bio1,Bio12,Bio15,slope,sand,ph,org),
                      select_AGB_Feld_RegOc$best$MEM.select) 
###################################################################################################################
###################################################################################################################
###################################################################################################################

###################################################################################################################
############################################################################################################
#Clean the environment



rm(select_AGB_Feld_RegAf)
rm(select_AGB_Feld_RegSA)
rm(select_AGB_Feld_RegAs)
rm(select_AGB_Feld_RegOc)


rm(res_AGB_Feld_RegAf)
rm(res_AGB_Feld_RegAs)
rm(res_AGB_Feld_RegSA)
rm(res_AGB_Feld_RegOc)


```
##Export
```{r include=FALSE}
# 
# fwrite(bestMEM_DBHqmAf,"bestMEM_DBHqmAf_WC.csv")
# fwrite(bestMEM_DBHqmSA,"bestMEM_DBHqmSA_WC.csv")
# fwrite(bestMEM_DBHqmAs,"bestMEM_DBHqmAs_WC.csv")
# fwrite(bestMEM_DBHqmOc,"bestMEM_DBHqmOc_WC.csv")
# fwrite(bestMEM_DBHqmNA,"bestMEM_DBHqmNA_WC.csv")
# 
# 
# 
# fwrite(bestMEM_BAAf,"bestMEM_BAAf_WC.csv")
# fwrite(bestMEM_BASA,"bestMEM_BASA_WC.csv")
# fwrite(bestMEM_BAAs,"bestMEM_BAAs_WC.csv")
# fwrite(bestMEM_BAOc,"bestMEM_BAOc_WC.csv")
# fwrite(bestMEM_BANA,"bestMEM_BANA_WC.csv")
# 
# 
# 
# fwrite(bestMEM_SDAf,"bestMEM_SDAf_WC.csv")
# fwrite(bestMEM_SDSA,"bestMEM_SDSA_WC.csv")
# fwrite(bestMEM_SDAs,"bestMEM_SDAs_WC.csv")
# fwrite(bestMEM_SDOc,"bestMEM_SDOc_WC.csv")
# fwrite(bestMEM_SDNA,"bestMEM_SDNA_WC.csv")
# 
# 
# 
# fwrite(bestMEM_WDbaAf,"bestMEM_WDbaAf_WC.csv")
# fwrite(bestMEM_WDbaSA,"bestMEM_WDbaSA_WC.csv")
# fwrite(bestMEM_WDbaAs,"bestMEM_WDbaAs_WC.csv")
# fwrite(bestMEM_WDbaOc,"bestMEM_WDbaOc_WC.csv")
# fwrite(bestMEM_WDbaNA,"bestMEM_WDbaNA_WC.csv")
# 
# 
# 
# 
# 
# fwrite(bestMEM_AGB_Feld_PanAf,"bestMEM_AGB_Feld_PanAf_WC.csv")
# fwrite(bestMEM_AGB_Feld_PanSA,"bestMEM_AGB_Feld_PanSA_WC.csv")
# fwrite(bestMEM_AGB_Feld_PanAs,"bestMEM_AGB_Feld_PanAs_WC.csv")
# fwrite(bestMEM_AGB_Feld_PanOc,"bestMEM_AGB_Feld_PanOc_WC.csv")
# fwrite(bestMEM_AGB_Feld_PanNA,"bestMEM_AGB_Feld_PanNA_WC.csv")
# 
# 
# 
# fwrite(bestMEM_AGB_Feld_ContAf,"bestMEM_AGB_Feld_ContAf_WC.csv")
# fwrite(bestMEM_AGB_Feld_ContSA,"bestMEM_AGB_Feld_ContSA_WC.csv")
# fwrite(bestMEM_AGB_Feld_ContAs,"bestMEM_AGB_Feld_ContAs_WC.csv")
# fwrite(bestMEM_AGB_Feld_ContOc,"bestMEM_AGB_Feld_ContOc_WC.csv")
# 
# 
# fwrite(bestMEM_AGB_Feld_RegAf,"bestMEM_AGB_Feld_RegAf_WC.csv")
# fwrite(bestMEM_AGB_Feld_RegSA,"bestMEM_AGB_Feld_RegSA_WC.csv")
# fwrite(bestMEM_AGB_Feld_RegAs,"bestMEM_AGB_Feld_RegAs_WC.csv")
# fwrite(bestMEM_AGB_Feld_RegOc,"bestMEM_AGB_Feld_RegOc_WC.csv")
```


##Importation
```{r include=FALSE}

#bestMEM_DBHqmAf<-fread("bestMEM_DBHqmAf_WC.csv")
#bestMEM_DBHqmSA<-fread("bestMEM_DBHqmSA_WC.csv")
#bestMEM_DBHqmAs<-fread("bestMEM_DBHqmAs_WC.csv")
#bestMEM_DBHqmOc<-fread("bestMEM_DBHqmOc_WC.csv")
#bestMEM_DBHqmNA<-fread("bestMEM_DBHqmNA_WC.csv")


#bestMEM_BAAf<-fread("bestMEM_BAAf_WC.csv")
#bestMEM_BASA<-fread("bestMEM_BASA_WC.csv")
#bestMEM_BAAs<-fread("bestMEM_BAAs_WC.csv")
#bestMEM_BAOc<-fread("bestMEM_BAOc_WC.csv")
#bestMEM_BANA<-fread("bestMEM_BANA_WC.csv")


#bestMEM_SDAf<-fread("bestMEM_SDAf_WC.csv")
#bestMEM_SDSA<-fread("bestMEM_SDSA_WC.csv")
#bestMEM_SDAs<-fread("bestMEM_SDAs_WC.csv")
#bestMEM_SDOc<-fread("bestMEM_SDOc_WC.csv")
#bestMEM_SDNA<-fread("bestMEM_SDNA_WC.csv")

#bestMEM_WDbaAf<-fread("bestMEM_WDbaAf_WC.csv")
#bestMEM_WDbaSA<-fread("bestMEM_WDbaSA_WC.csv")
#bestMEM_WDbaAs<-fread("bestMEM_WDbaAs_WC.csv")
#bestMEM_WDbaOc<-fread("bestMEM_WDbaOc_WC.csv")
#bestMEM_WDbaNA<-fread("bestMEM_WDbaNA_WC.csv")


#bestMEM_AGB_Feld_PanAf<-fread("bestMEM_AGB_Feld_PanAf_WC.csv")
#bestMEM_AGB_Feld_PanSA<-fread("bestMEM_AGB_Feld_PanSA_WC.csv")
#bestMEM_AGB_Feld_PanAs<-fread("bestMEM_AGB_Feld_PanAs_WC.csv")
#bestMEM_AGB_Feld_PanOc<-fread("bestMEM_AGB_Feld_PanOc_WC.csv")
#bestMEM_AGB_Feld_PanNA<-fread("bestMEM_AGB_Feld_PanNA_WC.csv")


#bestMEM_AGB_Feld_ContAf<-fread("bestMEM_AGB_Feld_ContAf_WC.csv")
#bestMEM_AGB_Feld_ContSA<-fread("bestMEM_AGB_Feld_ContSA_WC.csv")
#bestMEM_AGB_Feld_ContAs<-fread("bestMEM_AGB_Feld_ContAs_WC.csv")
#bestMEM_AGB_Feld_ContOc<-fread("bestMEM_AGB_Feld_ContOc_WC.csv")

#bestMEM_AGB_Feld_RegAf<-fread("bestMEM_AGB_Feld_RegAf_WC.csv")
#bestMEM_AGB_Feld_RegSA<-fread("bestMEM_AGB_Feld_RegSA_WC.csv")
#bestMEM_AGB_Feld_RegAs<-fread("bestMEM_AGB_Feld_RegAs_WC.csv")
#bestMEM_AGB_Feld_RegOc<-fread("bestMEM_AGB_Feld_RegOc_WC.csv")
```

#3. Multiple Linear Regression 

##3.1. DBHqm

###a) MLR Model with MEMs

```{r include=FALSE}


##Africa

#
DBHqmAf_F=lm(DBHqm~., data=bestMEM_DBHqmAf)
summary(DBHqmAf_F)


rse<-summary(DBHqmAf_F)$sigma
r_squared<-summary(DBHqmAf_F)$r.squared
mean<-data_Af[,mean(DBHqm),]
results<-tidy(DBHqmAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="DBH_qm",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]

results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(DBHqmAf_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "DBHqm", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(test)
rm(test)
##South-America

#
DBHqmSA_F=lm(DBHqm~., data=bestMEM_DBHqmSA)
summary(DBHqmSA_F)


rse<-summary(DBHqmSA_F)$sigma
r_squared<-summary(DBHqmSA_F)$r.squared
mean<-data_SA[,mean(DBHqm),]
results<-tidy(DBHqmSA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="DBH_qm",area="south_america",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(DBHqmSA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "DBHqm", area="south_america",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##Asia 

#
DBHqmAs_F=lm(DBHqm~., data=bestMEM_DBHqmAs)
summary(DBHqmAs_F)


rse<-summary(DBHqmAs_F)$sigma
r_squared<-summary(DBHqmAs_F)$r.squared
mean<-data_As[,mean(DBHqm),]
results<-tidy(DBHqmAs_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="DBH_qm",area="asia",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(DBHqmAs_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "DBHqm", area="asia",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##Oceania

#
DBHqmOc_F=lm(DBHqm~., data=bestMEM_DBHqmOc)
summary(DBHqmOc_F)


rse<-summary(DBHqmOc_F)$sigma
r_squared<-summary(DBHqmOc_F)$r.squared
mean<-data_Oc[,mean(DBHqm),]
results<-tidy(DBHqmOc_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="DBH_qm",area="oceania",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(DBHqmOc_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "DBHqm", area="oceania",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##north America

#
DBHqmNA_F=lm(DBHqm~., data=bestMEM_DBHqmNA)
summary(DBHqmNA_F)


rse<-summary(DBHqmNA_F)$sigma
r_squared<-summary(DBHqmNA_F)$r.squared
mean<-data_NA[,mean(DBHqm),]
results<-tidy(DBHqmNA_F, conf.int = TRUE) 

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="DBH_qm",area="north America",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(DBHqmNA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "DBHqm", area="north America",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)
```


##3.2. BA

###a) MLR Model with MEMs

```{r include=FALSE}

##Africa

#
BAAf_F=lm(BA~., data=bestMEM_BAAf)
summary(BAAf_F)


rse<-summary(BAAf_F)$sigma
r_squared<-summary(BAAf_F)$r.squared
mean<-data_Af[,mean(BA),]
results<-tidy(BAAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="BA",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(BAAf_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "BA", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##South-America

#
BASA_F=lm(BA~., data=bestMEM_BASA)
summary(BASA_F)


rse<-summary(BASA_F)$sigma
r_squared<-summary(BASA_F)$r.squared
mean<-data_SA[,mean(BA),]
results<-tidy(BASA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="BA",area="south_america",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(BASA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "BA", area="south_america", pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##Asia 

#
BAAs_F=lm(BA~., data=bestMEM_BAAs)
summary(BAAs_F)


rse<-summary(BAAs_F)$sigma
r_squared<-summary(BAAs_F)$r.squared
mean<-data_As[,mean(BA),]
results<-tidy(BAAs_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="BA",area="asia",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(BAAs_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "BA", area="asia",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##Oceania

#
BAOc_F=lm(BA~., data=bestMEM_BAOc)
summary(BAOc_F)


rse<-summary(BAOc_F)$sigma
r_squared<-summary(BAOc_F)$r.squared
mean<-data_Oc[,mean(BA),]
results<-tidy(BAOc_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="BA",area="oceania",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(BAOc_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "BA", area="oceania",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##north America

#
BANA_F=lm(BA~., data=bestMEM_BANA)
summary(BANA_F)


rse<-summary(BANA_F)$sigma
r_squared<-summary(BANA_F)$r.squared
mean<-data_NA[,mean(BA),]
results<-tidy(BANA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="BA",area="north America",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(BANA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "BA", area="north America",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


```


##3.3. SD

###a) MLR Model with MEMs

```{r include=FALSE}
##Africa

#
SDAf_F=lm(SD~., data=bestMEM_SDAf)
summary(SDAf_F)


rse<-summary(SDAf_F)$sigma
r_squared<-summary(SDAf_F)$r.squared
mean<-data_Af[,mean(SD),]
results<-tidy(SDAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="SD",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(SDAf_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "SD", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##South-America

#
SDSA_F=lm(SD~., data=bestMEM_SDSA)
summary(SDSA_F)


rse<-summary(SDSA_F)$sigma
r_squared<-summary(SDSA_F)$r.squared
mean<-data_SA[,mean(SD),]
results<-tidy(SDSA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="SD",area="south_america",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(SDSA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "SD", area="south_america",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##Asia 

#
SDAs_F=lm(SD~., data=bestMEM_SDAs)
summary(SDAs_F)


rse<-summary(SDAs_F)$sigma
r_squared<-summary(SDAs_F)$r.squared
mean<-data_As[,mean(SD),]
results<-tidy(SDAs_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="SD",area="asia",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)


test<-as.data.table(as.numeric(summary(SDAs_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "SD", area="asia",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##oceania

#
SDOc_F=lm(SD~., data=bestMEM_SDOc)
summary(SDOc_F)


rse<-summary(SDOc_F)$sigma
r_squared<-summary(SDOc_F)$r.squared
mean<-data_Oc[,mean(SD),]
results<-tidy(SDOc_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="SD",area="oceania",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)


test<-as.data.table(as.numeric(summary(SDOc_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "SD", area="oceania",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##north America

#
SDNA_F=lm(SD~., data=bestMEM_SDNA)
summary(SDNA_F)


rse<-summary(SDNA_F)$sigma
r_squared<-summary(SDNA_F)$r.squared
mean<-data_NA[,mean(SD),]
results<-tidy(SDNA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="SD",area="north America",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)


test<-as.data.table(as.numeric(summary(SDNA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "SD", area="north America",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


```

##3.4. WDba

###a)  MLR Model with MEMs

```{r include=FALSE}
##Africa

#
WDbaAf_F=lm(WDba~., data=bestMEM_WDbaAf)
summary(WDbaAf_F)


rse<-summary(WDbaAf_F)$sigma
r_squared<-summary(WDbaAf_F)$r.squared
mean<-data_Af[,mean(WDba),]
results<-tidy(WDbaAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="WDba",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(WDbaAf_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "WDba", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##South-America

#
WDbaSA_F=lm(WDba~., data=bestMEM_WDbaSA)
summary(WDbaSA_F)


rse<-summary(WDbaSA_F)$sigma
r_squared<-summary(WDbaSA_F)$r.squared
mean<-data_SA[,mean(WDba),]
results<-tidy(WDbaSA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="WDba",area="south_america",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(WDbaSA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "WDba", area="south_america", pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)



##Asia 

#
WDbaAs_F=lm(WDba~., data=bestMEM_WDbaAs)
summary(WDbaAs_F)


rse<-summary(WDbaAs_F)$sigma
r_squared<-summary(WDbaAs_F)$r.squared
mean<-data_As[,mean(WDba),]
results<-tidy(WDbaAs_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="WDba",area="asia",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(WDbaAs_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "WDba", area="asia",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##oceania

#
WDbaOc_F=lm(WDba~., data=bestMEM_WDbaOc)
summary(WDbaOc_F)


rse<-summary(WDbaOc_F)$sigma
r_squared<-summary(WDbaOc_F)$r.squared
mean<-data_Oc[,mean(WDba),]
results<-tidy(WDbaOc_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="WDba",area="oceania",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(WDbaOc_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "WDba", area="oceania",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##north America

#
WDbaNA_F=lm(WDba~., data=bestMEM_WDbaNA)
summary(WDbaNA_F)


rse<-summary(WDbaNA_F)$sigma
r_squared<-summary(WDbaNA_F)$r.squared
mean<-data_NA[,mean(WDba),]
results<-tidy(WDbaNA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="SC",sub_rep="WDba",area="north America",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(WDbaNA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "SC" , sub_rep = "WDba", area="north America",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


```


##3.6. AGB_Feld_Pan

###a) MLR Model with MEMs

```{r include=FALSE}
##Africa

#
AGB_Feld_PanAf_F=lm(AGB_Feld_Pan~., data=bestMEM_AGB_Feld_PanAf)
summary(AGB_Feld_PanAf_F)


rse<-summary(AGB_Feld_PanAf_F)$sigma
r_squared<-summary(AGB_Feld_PanAf_F)$r.squared
mean<-data_Af[,mean(AGB_Feld_Pan),]
results<-tidy(AGB_Feld_PanAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Pan",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_PanAf_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Pan", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)





##South-America

#
AGB_Feld_PanSA_F=lm(AGB_Feld_Pan~., data=bestMEM_AGB_Feld_PanSA)
summary(AGB_Feld_PanSA_F)



rse<-summary(AGB_Feld_PanSA_F)$sigma
r_squared<-summary(AGB_Feld_PanSA_F)$r.squared
mean<-data_SA[,mean(AGB_Feld_Pan),]
results<-tidy(AGB_Feld_PanSA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Pan",area="south_america",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_PanSA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Pan", area="south_america",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)



##Asia 

#
AGB_Feld_PanAs_F=lm(AGB_Feld_Pan~., data=bestMEM_AGB_Feld_PanAs)
summary(AGB_Feld_PanAs_F)


rse<-summary(AGB_Feld_PanAs_F)$sigma
r_squared<-summary(AGB_Feld_PanAs_F)$r.squared
mean<-data_As[,mean(AGB_Feld_Pan),]
results<-tidy(AGB_Feld_PanAs_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Pan",area="asia",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15,slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_PanAs_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Pan", area="asia",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##oceania

#
AGB_Feld_PanOc_F=lm(AGB_Feld_Pan~., data=bestMEM_AGB_Feld_PanOc)
summary(AGB_Feld_PanOc_F)


rse<-summary(AGB_Feld_PanOc_F)$sigma
r_squared<-summary(AGB_Feld_PanOc_F)$r.squared
mean<-data_Oc[,mean(AGB_Feld_Pan),]
results<-tidy(AGB_Feld_PanOc_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Pan",area="oceania",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15,slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_PanOc_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Pan", area="oceania",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##north America

#
AGB_Feld_PanNA_F=lm(AGB_Feld_Pan~., data=bestMEM_AGB_Feld_PanNA)
summary(AGB_Feld_PanNA_F)


rse<-summary(AGB_Feld_PanNA_F)$sigma
r_squared<-summary(AGB_Feld_PanNA_F)$r.squared
mean<-data_NA[,mean(AGB_Feld_Pan),]
results<-tidy(AGB_Feld_PanNA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Pan",area="north America",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15,slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_PanNA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Pan", area="north America",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


```


##3.7. AGB_Feld_Cont

###a) MLR Model with MEMs

```{r include=FALSE}
##Africa

#
AGB_Feld_ContAf_F=lm(AGB_Feld_Cont~., data=bestMEM_AGB_Feld_ContAf)
summary(AGB_Feld_ContAf_F)

rse<-summary(AGB_Feld_ContAf_F)$sigma
r_squared<-summary(AGB_Feld_ContAf_F)$r.squared
mean<-data_Af_AGB_Cont[,mean(AGB_Feld_Cont),]
results<-tidy(AGB_Feld_ContAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Cont",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_ContAf_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Cont", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)



##South-America

#
AGB_Feld_ContSA_F=lm(AGB_Feld_Cont~., data=bestMEM_AGB_Feld_ContSA)
summary(AGB_Feld_ContSA_F)

rse<-summary(AGB_Feld_ContSA_F)$sigma
r_squared<-summary(AGB_Feld_ContSA_F)$r.squared
mean<-data_SA_AGB_Cont[,mean(AGB_Feld_Cont),]
results<-tidy(AGB_Feld_ContSA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Cont",area="south_america",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area, Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_ContSA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Cont", area="south_america",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##Asia 

#
AGB_Feld_ContAs_F=lm(AGB_Feld_Cont~., data=bestMEM_AGB_Feld_ContAs)
summary(AGB_Feld_ContAs_F)

rse<-summary(AGB_Feld_ContAs_F)$sigma
r_squared<-summary(AGB_Feld_ContAs_F)$r.squared
mean<-data_As_AGB_Cont[,mean(AGB_Feld_Cont),]
results<-tidy(AGB_Feld_ContAs_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Cont",area="asia",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15,slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_ContAs_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Cont", area="asia",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##oceania

#
AGB_Feld_ContOc_F=lm(AGB_Feld_Cont~., data=bestMEM_AGB_Feld_ContOc)
summary(AGB_Feld_ContOc_F)

rse<-summary(AGB_Feld_ContOc_F)$sigma
r_squared<-summary(AGB_Feld_ContOc_F)$r.squared
mean<-data_Oc_AGB_Cont[,mean(AGB_Feld_Cont),]
results<-tidy(AGB_Feld_ContOc_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Cont",area="oceania",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15,slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_ContOc_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Cont", area="oceania",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

```

##3.8. AGB_Feld_Re


###a) MLR Model with MEMs

```{r include=FALSE}
##Africa

#
AGB_Feld_RegAf_F=lm(AGB_Feld_Reg~., data=bestMEM_AGB_Feld_RegAf)
summary(AGB_Feld_RegAf_F)


rse<-summary(AGB_Feld_RegAf_F)$sigma
r_squared<-summary(AGB_Feld_RegAf_F)$r.squared
mean<-data_Af_AGB_Reg[,mean(AGB_Feld_Reg),]
results<-tidy(AGB_Feld_RegAf_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Reg",area="africa",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_RegAf_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Reg", area="africa",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)

##South-America

#
AGB_Feld_RegSA_F=lm(AGB_Feld_Reg~., data=bestMEM_AGB_Feld_RegSA)
summary(AGB_Feld_RegSA_F)

rse<-summary(AGB_Feld_RegSA_F)$sigma
r_squared<-summary(AGB_Feld_RegSA_F)$r.squared
mean<-data_SA_AGB_Reg[,mean(AGB_Feld_Reg),]
results<-tidy(AGB_Feld_RegSA_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Reg",area="south_america",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_RegSA_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Reg", area="south_america",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)


##Asia 

#
AGB_Feld_RegAs_F=lm(AGB_Feld_Reg~., data=bestMEM_AGB_Feld_RegAs)
summary(AGB_Feld_RegAs_F)

rse<-summary(AGB_Feld_RegAs_F)$sigma
r_squared<-summary(AGB_Feld_RegAs_F)$r.squared
mean<-data_As_AGB_Reg[,mean(AGB_Feld_Reg),]
results<-tidy(AGB_Feld_RegAs_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Reg",area="asia",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_RegAs_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Reg", area="asia",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)



##oceania

#
AGB_Feld_RegOc_F=lm(AGB_Feld_Reg~., data=bestMEM_AGB_Feld_RegOc)
summary(AGB_Feld_RegOc_F)

rse<-summary(AGB_Feld_RegOc_F)$sigma
r_squared<-summary(AGB_Feld_RegOc_F)$r.squared
mean<-data_Oc_AGB_Reg[,mean(AGB_Feld_Reg),]
results<-tidy(AGB_Feld_RegOc_F, conf.int = TRUE)

setDT(results)
results<-as.data.table(t(results[2:8][p.value>=0.05,estimate:=NA]))

results<-row_to_names(results,row_number=1)
results[,`:=`(rep="AGB",sub_rep="AGB_Feld_Reg",area="oceania",r_squared=r_squared,RMSE=(rse/mean)*100,est=NA)]
results$est<-as.character(results$est)
results[1,est:="estimate"]
results[2,est:="std.error"]
results[3,est:="statistic"]
results[4,est:="p.value"]
results[5,est:="conf.low"]
results[6,est:="conf.high"]
end<-rbind(end,results[,.(rep, sub_rep, area,  Bio1, Bio12, Bio15, slope, sand, ph, org,r_squared,RMSE,est),])

rm(rse)
rm(mean)
rm(r_squared)
rm(results)

test<-as.data.table(as.numeric(summary(AGB_Feld_RegOc_F)$coefficients[,4]))
test<-test[2:8]
test[, `:=`(rep = "AGB" , sub_rep = "AGB_Feld_Reg", area="oceania",  pvalue=V1,var_pred=c("Bio1","Bio12","Bio15","slope","sand","ph","org"))][,V1:=NULL,]
end2<-rbind(end2,test)
rm(test)
```
##Export of the table

```{r}
end[,source:="WC",]
end2[,source:="WC",]

fwrite(end,"end_stand_WC.csv")
fwrite(end2,"end2_stand_WC.csv")


```

```{r}
```