---
title: "ACP"
output: html_document
date: "2024-03-01"
---

#Importation + packages

We reduced the initial set of available environmental variables (19 bioclimatic variables derived 
from the WorldClim dataset59 , two topographic and six soil variables), prior to running our models to ensure limited collinearity while retaining complementary climatic, topographic and edaphic elements (see below). To do so, we first examined the pairwise correlations between the variables and excluded one variable from each pair with correlation coefficients greater than or equal to 0.7. We then conducted a principal component analysis (PCA) based on a correlation matrix and applied a clustering analysis (i.e., Ward’s minimum variance clustering method) on a Euclidean distance matrix derived from the coordinates of the environmental variables on the first four PCA axes (describing 73% of the total PCA inertia)70  (Extended Data Figure 6).This was carried out using the vegan and stats R package71 

Note  The variables bio1 to bio19 correspond to the bioclimatic variables from the WorldClim dataset; in this demonstration, however, their values were randomly generated for illustrative purposes only.
```{r}
rm(list=ls()) 

setwd("C:/Users/u237004/Documents/1_Boulot_SC/2_Papier Pan/Final_Nature/Code/8_Graph/")

##Packages
library(data.table)
library(ggplot2)
library(plyr)#mu
library(stringr)
#library(ggpubr)
#library(cowplot)
library(multcomp)
#library(stats)
library(grid)
library(gridExtra)
#Une légende pour tous
get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}
library(flextable)
library(vegan)

##Importation

plot_var6<-fread("Pantropical_dataset_2076plots_V2_N_55_1_SOIL.csv")
plot_var6<-plot_var6[!elevation.y>=1000]
plot_var6<-plot_var6[!is.na(Bio1_WC)]
#choix<-fread("ACP-Choix_WC.csv")
#FOR DEMONSTRATION####################################################################################
# Définir le nombre de lignes
n <- 43

# Créer un data.frame avec des colonnes bio1 à bio19 remplies de valeurs aléatoires
set.seed(123)  # Pour reproductibilité
bio_data <- as.data.frame(matrix(runif(n * 19, min = 0, max = 100), nrow = n))
colnames(bio_data) <- paste0("bio", 1:19)

# Afficher les premières lignes du tableau
head(bio_data)

data<-cbind(plot_var6,bio_data)




```

##Correlation
```{r}
#Avec toutes 

summary(plot_var6)

pan<-data[!is.na(bio1),.(bio1,bio2,bio3,bio4,bio5,bio6,bio7,bio8,bio9,bio10,bio11,bio12,bio13,bio14,bio15,bio16,bio17,bio18,bio19,bulk,clay,org,ph,sand,water,slope,elevation.y)]

# 
# pan<-result[!is.na(bio1),.(bio1,bio12,bio15,org,ph,sand,slope,Proportion)]

library(corrplot)
pan<-cor(pan)

corrplot(pan, method="circle")
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
p.mat <- cor.mtest(pan)
corrplot(pan, type="upper", order="hclust",method="number", 
         p.mat = p.mat, sig.level = 0.01,number.cex = 0.7)


```
##c) ACPs 


###**ACP**: Ordination sur des variables quantitatives !

Enlever les NAs avant !!!!! 

```{r}
pca<-vegan::rda(data[!is.na(bio1),.(bio1,bio4,bio12,bio14,bio15,bio18,bulk,clay,org,ph,sand,water,slope)],scale=TRUE)#scale=TRUE spécifie qu'on veut travailler sur une matrice de corrélation et non de covariance. 
summary(pca)
#pca<-vegan::rda(choix[!is.na(bio1),.(bulk,clay,org,ph,sand,water,slope,elevation.y)],scale=TRUE)#scale=TRUE spécifie qu'on veut travailler sur une matrice de corrélation et non de covariance. 
#summary(pca)
```

   

##d) Clustering

Selon Numerical ecology with R !
                                    Ward’s Minimum Variance Clustering




```{r}
#Methode "Ward.D2" avec les 6 axes principaux: 91.3%
coord<-vegan::scores(pca,choices=c(1,2,3,4),display="sp")
d1<-vegan::vegdist(coord, method="euclidean")

cluster<-stats::hclust(d1,method="ward.D2")
plot(cluster,main="Ward.D2 method with 6 dimensions",hang=-1)
cluster.3gr_ward2_6<-cutree(cluster,7)
cluster.3gr_ward2_6

cluster.3gr.label_ward2_6<-paste(substr(rownames(coord),1,19),cluster.3gr_ward2_6)
plot(cluster,main="Ward.D2 method with 6 dimensions",hang=-1,labels=cluster.3gr.label_ward2_6)
rect.hclust(cluster,7)
```

