---
title: "SOl_topo"
output: html_document
date: "2024-01-18"
---



```{r}
# Clear the environment
rm(list=ls())
## Set working directory
setwd("C:/Users/u237004/Documents/1_Boulot_SC/2_Papier Pan/Final_Nature/Code/4_SOIL_TOPO")
# Load required packages for the functions
library(data.table)
library(raster)
```

#Importation
We import both the plot-level dataset and the environmental variables (selected soil and topographic variables, see Methods), which were extracted and processed using Google Earth Engine (GEE). Via GEE, for each plot, we extracted the corresponding values for each selected environmental variable.

Note : We provide the full Google Earth Engine (GEE) code used to extract soil and topographic variables for our plots (i.e. to obtain the plot_data.csv) as a .txt (file see "GEE.txt"). For demonstration purposes, however, all values used here are entirely randomly generated and do not reflect real environmental conditions.
```{r}

soil<-fread("plots_data.csv")
plot<-fread("Pantropical_dataset_2076plots_V2_N_55_1.csv")
summary(soil)
#mergeage
plot2<-merge(plot,soil[,.(PLT_trois_bis,bulk=bulk,clay,org=org,ph=ph,sand,water,slope,elevation)],by="PLT_trois_bis", all.x=TRUE)

plot2[is.na(bulk),.(unique(LAT),unique(LON),unique(source),unique(Continent)),by='PLT_trois_bis'] # 3 NAs
summary(plot2)

plot3<-plot2[!is.na(bulk)]

```

FOR DEMONSTRATION
```{r}
plot<-fread("Pantropical_dataset_2076plots_V2_N_55_1.csv")

set.seed(123)  

n <- nrow(plot)

plot[, `:=`(
  bulk = runif(n, 0.8, 1.6),          
  clay = runif(n, 10, 60),             
  org = runif(n, 0.5, 15),              
  ph = runif(n, 3.5, 7.5),             
  sand = runif(n, 20, 80),             
  water = runif(n, 5, 50),              
  slope = runif(n, 0, 45),             
  elevation.y = runif(n, 0, 1005)       
)]

```
#Export of the table

```{r}

fwrite(plot,"Pantropical_dataset_2076plots_V2_N_55_1_SOIL.csv")
```